On exponential sums arising from the classical doubling method

### 2025-03-20 paper.tex
Torus character

For a torus theta pair $(T,\theta)$ with associated Frobenius conjugacy classes $w \in W(\algebraicGroup{T})$ and $(s) \subset G^*$ and an embedding $\rho:G^* \to \GL_n$.  Fix a Frobenius stable maximal torus $\algebraicGroup{T}^* \subset G^*$ and a Frobenius stable maximal torus $\algebraicGroup{T} \subset \GL_n$ which contains $\rho(\algebraicGroup{T}^*)$. Let $\tilde{T}$ be the torus of $\GL_n$ corresponding to the Frobenius conjugacy class of $\rho(w) \in W(\algebraicGroup{T})$ and $\tilde{\theta}$ such that $(\rho(s)) = (s_{\tilde{T},\tilde{\theta}})$. Define
\[
    g_{T,\rho}(\theta,\psi,\chi) := \varepsilon_{\algebraicGroup{
    \tilde{T}}}\sum_{t\in \tilde{T}} \tilde{\theta}(t)\chi(\det(t))\psi(\trace(t)).
\]
The following lemma shows that this is well defined.

@@

In particular to analyze $g_{T,\rho}(\theta,\psi,\chi)$ for these $\rho$, we need to understand what torus theta pair of $\GL$ corresponds to $\phi((s))$ under a map $\phi(x) = (x,-x)$:
%The following computation in the proof of theorem \ref{lem:indep_geo_conj}.

>>>>

For a torus character pair $(T,\theta)$ with associated Frobenius conjugacy classes $w \in W(\algebraicGroup{T})$ and $(s) \subset G^*$ and an embedding $\rho:G^* \to \GL_n$.  Fix a Frobenius stable maximal torus $\algebraicGroup{T}^* \subset G^*$ and a Frobenius stable maximal torus $\algebraicGroup{T} \subset \GL_n$ which contains $\rho(\algebraicGroup{T}^*)$. Let $\tilde{T}$ be the torus of $\GL_n$ corresponding to the Frobenius conjugacy class of $\rho(w) \in W(\algebraicGroup{T})$ and $\tilde{\theta}$ such that $(\rho(s)) = (s_{\tilde{T},\tilde{\theta}})$. Define
\[
    g_{T,\rho}(\theta,\psi,\chi) := \varepsilon_{\algebraicGroup{
    \tilde{T}}}\sum_{t\in \tilde{T}} \tilde{\theta}(t)\chi(\det(t))\psi(\trace(t)).
\]
The following lemma shows that this is well defined.

@@

In particular to analyze $g_{T,\rho}(\theta,\psi,\chi)$ for these $\rho$, we need to understand what torus character pair of $\GL$ corresponds to $\phi((s))$ under a map $\phi(x) = (x,-x)$:
%The following computation in the proof of theorem \ref{lem:indep_geo_conj}.
